Supplementary Material for Asymmetry paper

### 2020-05-11 Supplementary/Sup_mat.Rmd
Updated plots

```{r drawdistributions, include = T, echo = F, fig.height = 3, fig.cap="Warren write some text."}
load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")

@@

plt_dists <- df_distributions %>% 
  mutate(diff = as.factor(diff)) %>% 
  ggplot(aes(x_vals, p)) + 
  geom_line(aes(colour = diff)) + 
  theme_bw() + 
  see::scale_color_flat() +
  guides(colour = guide_legend("Difference")) + 
  theme(
    axis.title = element_blank(),
    legend.position = "bottom"
  )

@@

The plot below the distributions shows the uncertainty surrounding the mean estimate for the smallest difference tested (5\%). After 15 participants, the uncertainty surrounding the estimate appears to plateau which demonstrates that the sample size of 21 was sufficient to detect the effect.

```{r  include = T, echo = F, fig.height = 3}

>>>>

```{r drawdistributions, include = T, echo = F, fig.height = 3, fig.cap="The left hand plot shows a histrogram for the empirical data from Clarke and Hunt (2016) with a line to show a beta distribution that had been fit to these data. The right hand plot shows how this distribution would change had the participants' mean position had been biased towards one of the side hoops to varying degrees."}
load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")

@@

plt_dists <- df_distributions %>% 
  mutate(diff = as.factor(diff)) %>% 
  ggplot(aes(x_vals, p)) + 
  geom_line(aes(colour = diff)) + 
  theme_bw() + 
  see::scale_color_flat() +
  guides(colour = guide_legend("Difference")) + 
  theme(
    axis.title = element_blank(),
    legend.title = element_blank(),
    legend.position = "right"
  )

@@

Figure \@ref(fig:HDIHoopSize) shows the uncertainty surrounding the mean estimate for the smallest difference tested (5\%). After 15 participants, the uncertainty surrounding the estimate appears to plateau which demonstrates that the sample size of 21 was sufficient to detect the effect.

```{r HDIHoopSize, include = T, echo = F, fig.height = 3, fig.cap="This figure shows how the 95% HDI around the mean difference for the smallest difference simulated (5%) changed with a larger sample size"}
